\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-22 syntactic-example.tex
Change Syntax for the Examplar usage.

We provide one example in its surface syntax as pseudocode, and their
meta-theory encoding. This example is computing the predecessor of a
mundane natural number, but we split the inductive definition into two
parts and making "O" and "S" standing alone.
"pred" will map $S~n \mapsto (n, S~n)$ and $O \mapsto (O, O)$, and thus a predecessor.\YZ{
  Using family polymorphism for adding  a successor constructor is unnatural.
  I suggest simply renaming the constructors and not mentioning the correspondence to natural numbers.
}

\begin{figure}[H]\label{fig:example-pseudocode}
\begin{minipage}[t]{0.5\linewidth}
\begin{minted}[escapeinside=@@]{Coq}
Family A.
 FInductive N := O : N. 
 (* Osig, sig₁, obj₁, sig₂,
    O₁, obj₂, sig₂', sl₁ *)
 Family handler.
   O :self[A].N × self[A].N 
     := (self[A].O, self[A].O).

 EndFamily. (* pN₁, handler₁, sig₃ *)
 FRecursor pred about self[A].N 
  motive (fun _ => self[A].N × self[A].N)
  using handler.
 (* pred
  : self[A].N → self[A].N × self[A].N *)
  (* predT, pred₁, sig₄, sig₄', sl₄ *) 
 k := self[A].pred self[A].O 
(* pN₂, sig₅ *)
EndFamily.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.45\linewidth}
\begin{minted}[escapeinside=@@]{Coq}
Family A₂ extends A.
 Extend FInductive N := S : N → N.
 (* Nsig, sig₁₁, inh₁, O₂, sig₂₁, inh₂, 
    sig₂₂, sig₂₁', sig₂₂', sl₂₂, inh₃ *)
 Extend Family handler.
   Inherit O. (* inhᵢₙ₀, pN₃ *)
   S : self[A].N × self[A].N
       → self[A].N × self[A].N 
     := fun (x,y) => (y, self[A₂].S y).
 EndFamily. (* inhᵢₙ, sig₃₁, inh₄*)
 Inherit pred.

  (* sig₄₁, inh₅, sl₄₁ *)
 Inherits k. 
 (* inh₆ *)
EndFamily.
    \end{minted}
  \end{minipage}\YZ{This figure needs updating; it should use the same syntax as in §3.}\YZreply{Also, this figure should contain an example of accessing a field outside its family.}
  \caption{Demonstrating Pseudo-Code}
\end{figure}

\begin{figure}
  \begin{minipage}{\linewidth}
    \begin{minted}{Coq}
      Inductive N :=
       | O : 1 -> (0 -> N) -> N 
       | S : 1 -> (1 -> N) -> N
      (* For example, Number 1 is encoded using
         1 = S () (fun _ -> O () (fun x -> elim-⊥ x)) *)
    \end{minted}
  \end{minipage}

>>>>

We provide one example in its surface syntax as pseudocode, and their
meta-theory encoding. This example is computing the predecessor of a
mundane natural number, but we split the inductive definition into two
parts and making "O" and "S" standing alone.
"pred" will map $S~n \mapsto (n, S~n)$ and $O \mapsto (O, O)$, and thus a predecessor.\YZ{
  Using family polymorphism for adding  a successor constructor is unnatural.
  I suggest simply renaming the constructors and not mentioning the correspondence to natural numbers.
}\EDJreply{I don't have a good idea for the renaming. What about you?}

\begin{figure}[!htb]\label{fig:example-pseudocode}
  \lstset{
      basicstyle=\fontsize{8}{8.5}\ttfamily,
  % numbers=left,
  }

  \begin{minipage}{\textwidth}
  \begin{multicols}{2}

  \definecolor{codecomment-color}{HTML}{0DA3FF}

  \begin{lstlisting} 
  Family A. [@\tanc{Coq-Example1-start}@]
  FInductive N := O : N. 
  (* [@ \tiny{Osig, sig₁, obj₁, sig₂,
     O₁, obj₂, sig₂', sl₁} @] *)

  FRecursion pred on N
    motive (fun _ => N × N).
  Case O := (O, O). 
  End pred. (* [@ \tiny{pN₁, handler₁, sig₃} @] *)
  (* pred : self[A].N → self[A].N × self[A].N *)
   (* [@ \tiny{predT, pred₁, sig₄, sig₄', sl₄} @] *) 
  k := pred O 
  (* [@ \tiny{pN₂, sig₅} @] *)  
  End A.[@\tanc{Coq-Example1-end}@]
  \end{lstlisting}

  \makeline[0pt]{Coq-Example1-start}{Coq-Example1-end}[codecomment-color!50]

  \columnbreak

  \definecolor{codecomment-color}{HTML}{5D030F}

  \begin{lstlisting}
  Family [@ \tiny{"A"$_2$} @] extends A. [@\tanc{Coq-Example2-start}@]
  FInductive N += S : N → N.
  (* [@ \tiny{Nsig, sig₁₁, inh₁, O₂, sig₂₁, inh₂, 
      sig₂₂, sig₂₁', sig₂₂', sl₂₂, inh₃} @] *)
  FRecursion pred.
  Inherit O. (* [@ \tiny{inhᵢₙ₀, pN₃} @] *)
  Case S := fun (x,y) => (y, S y).
  EndFamily. (* [@ \tiny{inhᵢₙ, sig₃₁, inh₄} @] *)
  Inherit pred.
    (* [@ \tiny{sig₄₁, inh₅, sl₄₁} @] *)
  Inherits k. 
  (* inh₆ *)
  End [@\tiny{"A"$_2$}@][@\tanc{Coq-Example2-end}@]
  \end{lstlisting}

  \makeline[.5\textwidth+9pt]{Coq-Example2-start}{Coq-Example2-end}[codecomment-color!50]

  \end{multicols}
  \end{minipage}

  \caption{Exemplar Compilation about Inductive Type, for STLC example}\label{fig:plugin-example2}
  \end{figure}

\YZreply{Also, this figure should contain an example of accessing a field outside its family.}
\begin{figure}
  \begin{minipage}{\linewidth}
    \begin{minted}{Coq}
      Inductive N :=
       | O : 1 -> (0 -> N) -> N 
       | S : 1 -> (1 -> N) -> N
      (* For example, Number 1 is encoded using
         1 = S () (fun _ -> O () (fun x -> elim-⊥ x)) *)
    \end{minted}
  \end{minipage}
